Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-29 paper/ijcai16.tex
paper: added future work

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces. Our approach relies on an
extension of max-margin learning to sets, and is
effective in the generation of a diverse set of configurations that can be used
to ask informative preference queries.  The main advantages of this
elicitation method are 1) its ability to elicit preferences and
provide recommendations in large configuration problems 2)
robustness with respect to erroneous feedback and 3)  ability to
encourage sparse utility functions. 
Experimental comparisons against
state-of-the-art Bayesian preference elicitation strategies confirm
its substantial computational advantages. For sparse utility
functions, the method compares favorably also in terms of utility loss.

>>>>

We presented a max-margin approach for efficient preference
elicitation in large configuration spaces. Our approach relies on an
extension of max-margin learning to sets, and is effective in the
generation of a diverse set of configurations that can be used to ask
informative preference queries.  The main advantages of this
elicitation method are 1) ability to provide recommendations in large
configuration problems 2) robustness with respect to erroneous
feedback and 3) ability to encourage sparse utility functions.
Experimental comparisons against state-of-the-art Bayesian preference
elicitation strategies confirm these advantages. Future work includes
extending the approach to truly hybrid scenarios (where real valued
attributes do not depend on categorical ones) and studying the
applicability of the setwise max-margin idea to other problems.
